Supporting Information for ``Nonparametric Block Bootstrap Kolmogorov--Smirnov Goodness-of-Fit Test''

### 2024-07-10 manuscript/manuscript.tex
finite dimensional convergence and tightness

The standard one-sample Kolmogorov--Smirnov (KS) test is widely
recognized as an effective good-of-fit test for continuous distributions.
Consider $X_1, ..., X_n$, a random sample of size~$n$ from some continuous
distribution and the null hypothesis $H_0$ that $X_i$'s follow a specific
hypothesized distribution~$F(x; \theta_0)$, where $\theta_0$ are the 
specified parameters
of the hypothesized distribution family.
If we let $F_n(t) = \sum_{i=1}^n I(X_i \le t) / n$ be the empirical cumulative
distribution function of the sample, where $I(\cdot)$ is the indicator
function, the KS test statistic takes the form
\[
  D_n = \sqrt{n} \sup_x | F_{n}(x) - F(x; \theta_0)|.
\]
As sample size $n\to \infty$, the distribution of $D_n$ converges to that of the
absolute value of standard Brownian bridge, which is known as the Kolmogorov
distribution \citep{stephens1974edf}. This distribution function is
precisely computable using contemporary statistical software
\citep{marsaglia2003evaluating}. The versatility of the KS test allows its
application across various domains, such as analyzing cosmic microwave
background radiation \citep{naess2012application}, monitoring the count rate of
radioactive data \citep{aslam2020introducing}, gear condition monitoring
\citep{andrade2001gear}, studying images of breast cancer tumors
\citep{demidenko2004kolmogorov}, and examining financial markets
\citep{lux2001turbulence}.

@@

Continue with the case where $X_i$'s are independent but the parameters
are unspecified. Denote by
$F^{(b)}_n$ the empirical distribution of the $b$th bootstrap sample and let
$\hat\theta^{(b)}_n$ be the parameter estimate based on the $b$th bootstrap 
sample. 
Using the bootstrap (asymptotic) theory, we can approximate the distribution of
$\sqrt{n}(F_n(x) - F(x; \theta_0))$ and
$\sqrt{n}(F(x; \hat\theta_n) - F(x; \theta_0))$
by that of $\sqrt{n}(F^{(b)}_n(x) - F_n(x))$ and
$\sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; \hat\theta_n))$, respectively.
Therefore, if we define
\begin{align*}
Y^{(b)}_n(x) &= \sqrt{n}(F^{(b)}_n(x) - F_n(x)) - 
               \sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; \hat\theta_n)) \\
             &= \sqrt{n}(F^{(b)}_n(x) - F(x; \hat\theta^{(b)}_n)) - 
               \sqrt{n}(F_n(x) - F(x; \hat\theta_n)),
\end{align*}
then $T^{(b)}_n := \sup_x|Y^{(b)}_n(x)|$ is the bootstrap statistic that is 
expected to approximate the distribution of $T_n$. 
We note that the term
$\sqrt{n}(F_n(x) - F(x; \hat\theta_n))$ is exactly the bias term considered in 
\citet{babu2004goodness}.

@@

\begin{proposition}\label{prop:Tnboot}
  As $1/l+l/n\rightarrow 0$,
  \[
    \big\vert \mathbb{P}(T_n^{(b)}\leq x \mid \{X_i: i = 1, \ldots, n\}) -
    \mathbb{P}(T_n\leq x) \big\vert
    \overset{a.s.}{\rightarrow} 0
  \]
  for any fixed $x$, where and $T_n^b$ is the the statistic computed 
  based on the bootstrap sample $\{X_i^{(b)}: i = 1, \ldots, n\}$.
\end{proposition}

Following the arguments in the proof of the Glivenko--Cantelli
Theorem, the result in Proposition~\ref{prop:Tnboot} can be further
strengthened to allow uniform convergence over $x$. That is,
\[
  \sup_x \big \vert
  \mathbb{P}(T_n^{(b)}\leq x \mid \{X_i: i = 1, \ldots, n\}) - \mathbb{P}(T_n\leq x) \big\vert
  \overset{a.s.}{\rightarrow} 0.
\]

@@

\subsection{Power}
The power of the proposed test is investigated with data generated from
distributions that are not in the hypothesized distribution family. 
We generated the same scheme of time series as we did in the size investigation,
but tested that the time series was from the other distribution.
Because the support of $N(8, 8)$ is
$(-\infty, \infty)$, but the support of $\Gamma(8, 1)$ is $(0, \infty)$, we used
the \textsl{truncdist} package \citep{truncdist} to truncate the series at 
values less than or equal to 0 when testing that the $N(8, 8)$ sample was
from $\Gamma(8, 1)$. For each setting for $F$, $\tau$, and $n$, we replicate the 
method $10000$ times 
to obtain a p-value $p_r$ for each $r \in \{1, \ldots, 10000\}$.  
The empirical rejection rates were obtained at a nominal significance level 0.05.

>>>>

The standard one-sample Kolmogorov--Smirnov (KS) test is widely
recognized as an effective good-of-fit test for continuous distributions.
Consider $X_1, ..., X_n$, a random sample of size~$n$ from some continuous
distribution and the null hypothesis $H_0$ that $X_i$'s follow a specific
hypothesized distribution~$F(x; \theta_0)$, where $\theta_0$ are the 
specified parameters
of the hypothesized distribution family.
If we let $F_n(t) = \sum_{i=1}^n \mathbf{1}(\{X_i \le t\} / n$ be the empirical cumulative
distribution function of the sample, where $\mathbf{1}\{\cdot\}$ is the indicator
function, the KS test statistic takes the form
\[
  D_n = \sqrt{n} \sup_x | F_{n}(x) - F(x; \theta_0)|.
\]
As sample size $n\to \infty$, the distribution of $D_n$ converges to that of the
absolute value of standard Brownian bridge, which is known as the Kolmogorov
distribution \citep{stephens1974edf}. This distribution function is
precisely computable using contemporary statistical software
\citep{marsaglia2003evaluating}. The versatility of the KS test allows its
application across various domains, such as analyzing cosmic microwave
background radiation \citep{naess2012application}, monitoring the count rate of
radioactive data \citep{aslam2020introducing}, gear condition monitoring
\citep{andrade2001gear}, studying images of breast cancer tumors
\citep{demidenko2004kolmogorov}, and examining financial markets
\citep{lux2001turbulence}.

@@

Continue with the case where $X_i$'s are independent but the parameters
are unspecified. Denote by
$F^{(b)}_n$ the empirical distribution of the $b$th bootstrap sample and let
$\hat\theta^{(b)}_n$ be the parameter estimate based on the $b$th bootstrap 
sample. 
Using the bootstrap (asymptotic) theory, we can approximate the distribution of
$\sqrt{n}(F_n(x) - F(x; \theta_0))$ and
$\sqrt{n}(F(x; \hat\theta_n) - F(x; \theta_0))$
by that of $\sqrt{n}(F^{(b)}_n(x) - F_n(x))$ and
$\sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; \hat\theta_n))$, respectively.
Therefore, if we define
\begin{align*}
Y^{(b)}_n(x) &= \sqrt{n}(F^{(b)}_n(x) - F_n(x)) - 
               \sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; \hat\theta_n)) \\
             &= \sqrt{n}(F^{(b)}_n(x) - F(x; \hat\theta^{(b)}_n)) - 
               \sqrt{n}(F_n(x) - F(x; \hat\theta_n)),
\end{align*}
then $T^{(b)}_n := \sup_x|Y^{(b)}_n(x)|$ is the bootstrap statistic that is 
expected to approximate the distribution of $T_n$. 
\eds{you have defined two $T_n$'s - perhaps different notation should be used
to differentiate the $T_n$ in the Intro and the $T_n$ in Section 2.1?  At least
clarify which $T_n$ you are referring to here.}\mc{addressed}
We note that the term
$\sqrt{n}(F_n(x) - F(x; \hat\theta_n))$ is exactly the bias term considered in 
\citet{babu2004goodness}.

@@

\begin{proposition}\label{prop:Tnboot}
  As $1/l+l/n\rightarrow 0$,
  \[
    \big\vert \mathbb{P}(T_n^{(b)}\leq x \mid \{X_i: i = 1, \ldots, n\}) -
    \mathbb{P}(T_n\leq x) \big\vert
    \overset{a.s.}{\rightarrow} 0
  \]
  for any fixed $x$, where and $T_n^{(b)}$ is the the statistic computed 
  based on the bootstrap sample $\{X_i^{(b)}: i = 1, \ldots, n\}$.
\end{proposition}

\eds{Is $T_n^*$ the same as $T_n^{(b)}$?  Can we replace the $t$ index with $i$ 
to be consistent with earlier notation?  Or use $t$ earlier when introducing
time-series data? ($t$ is used in the Simulation section below.)}\mc{I replaced
everything with $i$, I wasn't sure when to use $X_i$ or $\{X_i\}$}

Following the arguments in the proof of the Glivenko--Cantelli
Theorem, the result in Proposition~\ref{prop:Tnboot} can be further
strengthened to allow uniform convergence over $x$. That is,
\[
  \sup_x \big \vert
  \mathbb{P}(T_n^{(b)}\leq x|\{X_i: i = 1, \ldots, n\}) - \mathbb{P}(T_n\leq x) \big\vert
  \overset{a.s.}{\rightarrow} 0.
\]

\eds{Replace $X_{1:n}$ with $\{X_i: i = 1, \ldots, n\}$ or $\{X_t: t = 1, \ldots, n\}$?}
\mc{addressed}

@@

\subsection{Power}
The power of the proposed test is investigated with data generated from
distributions that are not in the hypothesized distribution family. 
We generated the same scheme of time series as we did in the size investigation,
but tested that the time series was from the other distribution.
Because the support of $N(8, 8)$ is
$(-\infty, \infty)$, but the support of $\Gamma(8, 1)$ is $(0, \infty)$, we used
the \textsl{truncdist} package \citep{truncdist} to truncate the series at 
values less than or equal to 0 when testing that the $N(8, 8)$ sample was
from $\Gamma(8, 1)$. For each setting for $F$, $\tau$, and $n$, we replicate the 
method $10000$ times 
to obtain a p-value $p_r$ for each $r \in \{1, \ldots, 10000\}$.  
\eds{1000 or  10000?}\mc{addressed}
The empirical rejection rates were obtained at a nominal significance level 0.05.
\eds{what do you mean by `actual' rejection rate? True rejection rate?  
I don't see the CI in Figure 2.}\mc{addressed}

### 2024-07-10 manuscript/supplement.tex
finite dimensional convergence and tightness

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{authblk}
\usepackage{algorithm}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{algpseudocode}
\usepackage{bbm}
\usepackage{bm}
\usepackage{caption}
\usepackage{color}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{float}
\usepackage{mathtools}
\usepackage{makecell}
\usepackage{multirow}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage{comment}
\usepackage{longtable}
\usepackage{rotating}
\usepackage{xcolor}
\usepackage{fullpage}

@@

\begin{proof}[Proof of Proposition~1]
We first derive the limiting distribution of the KS statistic under the null. 
Suppose $\hat{\theta}_n$ admits the expansion:
\begin{align}\label{eq-expan}
\hat{\theta}_n-\theta_0 = \frac{1}{n}\sum^{n}_{i=1}h(X_i;\theta_0) + 
\frac{1}{\sqrt{n}}R_n,    
\end{align}
where $h(\cdot;\theta_0)$ is the influence function with 
$\mathbb{E}[h(X_i;\theta_0)]=0$ and $R_n$ is the remainder term satisfying that
$R_n\overset{p}{\rightarrow} 0.$ Write $G_n(x):=\sqrt{n}(F_n(x) - 
F(x; \theta_0))$ 
and let $f(x;\theta)=\partial F(x;\theta)/\partial \theta$. We assume 
$\theta \in \mathbb{R}$ for ease of presentation.

Given any $x_1,\dots,x_m$ in the domain of $F$, by the CLT for weakly dependent 
time series, we have the joint convergence of 
$V_n:=(G_n(x_1),\dots,G_n(x_m),\sqrt{n}(\hat{\theta}_n-\theta_0))$
to some Gaussian limit, with the covariance matrix being 
$\Sigma_{m+1}=\lim_{n\rightarrow+\infty}\text{Cov}(V_n)$.
%\begin{align*}
%\Sigma_{m+1}=\begin{pmatrix}
%df & df & \cdots & df\\   
%df & df & \cdots & df\\ 
%\cdots & \cdots & \ddots & \cdots  \\ 
%df & df & \cdots & df
%\end{pmatrix}    
%\end{align*} 
Moreover, we can show the tightness of the process $G_n(x)$. 
For sufficiently small $\delta$, and leveraging the properties of weakly 
dependent sequences, we can show that
\[ \sup_{|x - y| < \delta} |G_n(x) - G_n(y)| = \sup_{|x - y| < \delta} 
\sqrt{n}|(F_n(x) - F(x)) - (F_n(y) - F(y))| \]
is small with high probability.
Specifically, since $F(x)$ is continuous, for small 
$\delta$, $|F(x) - F(y)|$ is small. For the empirical 
distribution function $F_n(x)$, the increments $|F_n(x) - F_n(y)|$ are 
also controlled. 
This implies that the process $G_n(x)$ does not exhibit large oscillations over 
small intervals, thus satisfying the criterion for tightness.
Therefore, we have
\begin{align*}
\begin{pmatrix}
G_n(x)  \\ 
\sqrt{n}(F(x;\hat{\theta}_n)-F(x;\theta_0))
\end{pmatrix}\Rightarrow
\begin{pmatrix}
G_{\infty}(x) \\
f(x;\theta_0)U
\end{pmatrix}
\end{align*}
jointly, where $G_{\infty}(x)$ is a Gaussian process with the covariance 
function defined as
\begin{align*}
\text{Cov}(G_{\infty}(x),G_{\infty}(x'))=& 
\lim_{n\rightarrow+\infty}\frac{1}{n}\sum^{n}_{i,j=1}
\text{Cov}(\mathbf{1}\{X_i\leq x\},\mathbf{1}\{X_j\leq x'\})
\\=& \sum^{+\infty}_{h=-\infty}\text{Cov}(\mathbf{1}\{X_{h}\leq x\},
\mathbf{1}\{X_0\leq x'\}),
\end{align*}
and $U\sim N(0,s^2)$ with 
\begin{align*}
s^2=\lim_{n\rightarrow+\infty}\frac{1}{n}\sum^{n}_{i,j=1}\text{Cov}(h(X_i,
\theta_0),h(X_j;\theta_0))
= \sum^{+\infty}_{h=-\infty}\text{Cov}(h(X_{h},\theta_0),h(X_0;\theta_0)),
\end{align*}
and the covariance between $U$ and $G_{\infty}(x)$ is given by
\begin{align*}
\text{Cov}(U,G_\infty(x))=&\lim_{n\rightarrow+\infty}
\frac{1}{n}\sum^{n}_{i,j=1}\text{Cov}(h(X_i,\theta_0),\mathbf{1}\{X_j\leq x\})
\\=&\sum^{+\infty}_{h=-\infty}
\text{Cov}(h(X_{h},\theta_0),\mathbf{1}\{X_0\leq x\}).
\end{align*}
By the continuous mapping theorem, we obtain
\begin{align*}
T_n \overset{d}{\rightarrow} \sup_x |G_{\infty}(x)+f(x;\theta_0)U|.    
\end{align*}

@@

Denote by $\mathbb{E}^{(b)}$, $\text{Var}^{(b)}$ and $\text{Cov}^{(b)}$
the expectation, variance and covariance conditional on 
$\{X_i: i = 1, \ldots, n\}$ in 
the bootstrap world. Assuming that $n=kl$ with $l$ being the block size and $k$ 
being the number of blocks, the bootstrap marginal distribution is 
\begin{align*}
\rho_n^{(b)}=\frac{1}{n}\sum^{k}_{j=1}\sum^{S_j+l-1}_{i=S_j} \delta_{X_i},    
\end{align*}
where $\delta_x$ denotes a point mass at $x$, and $S_1,\dots,S_k$ are i.i.d 
uniform on $\{1,\dots,n-l+1\}$. 
Define $G_n^{(b)}(x)$ in the same way as $G_n(x)$ with $X_1, \dots, X_n$ being 
replaced by the bootstrap samples %$\{X_i: i = 1, \ldots, n\}^{(b)}=\{X_1^{(b)},\dots,X_n^{(b)}\}$.
$X_1^{(b)},\dots,X_n^{(b)}.$

@@

For $\sqrt{n}(F(x;\hat{\theta}_n^{(b)}) - F(x;\hat{\theta}_0))$, using the 
first-order Taylor 
expansion around $\hat{\theta}_0$ similarly to what was done in 
\citet{kunsch1989jackknife}, we have:
\[
F(x;\hat{\theta}_n^{(b)}) \approx F(x;\hat{\theta}_0) + f(x; 
\hat{\theta}_0) (\hat{\theta}_n^{(b)} - \hat{\theta}_0),
\] so
\[
\sqrt{n}(F(x;\hat{\theta}_n^{(b)}) - F(x;\hat{\theta}_0)) \approx \sqrt{n} 
(F(x;\hat{\theta}_0) + f(x; 
\hat{\theta}_0) (\hat{\theta}_n^{(b)} - \hat{\theta}_0) - F(x;\hat{\theta}_0)) 
\approx
f(x; 
\hat{\theta}_0) \sqrt{n} (\hat{\theta}_n^{(b)} - \hat{\theta}_0).
\]

Substituting the expansion of $\hat{\theta}_n^{(b)}$:
\[
\sqrt{n} (\hat{\theta}_n^{(b)} - \hat{\theta}_0) = \frac{1}{\sqrt{n}} 
\sum_{i=1}^{n} 
h(X_i^{(b)}; \hat{\theta}_0) + R_n^{(b)}.
\]

Since $R_n^{(b)} \overset{p^{(b)}}{\rightarrow} 0$, 
\[
\sqrt{n}(F(x;\hat{\theta}_n^{(b)}) - F(x;\hat{\theta}_0)) \approx 
f(x; \hat{\theta}_0) \left( \frac{1}{\sqrt{n}} \sum_{i=1}^{n} h(X_i^{(b)}; 
\hat{\theta}_0) \right).
\]

The term $\frac{1}{\sqrt{n}} \sum_{i=1}^{n} h(X_i^{(b)}; \hat{\theta}_0)$ 
converges in distribution to a normal random variable $U$ with variance 
$s^2$.
We can show tightness of $G_n^{(b)}(x)$ similarly to how we established 
tightness of $G_n(x)$
The results then follow from the continuous mapping theorem.
\end{proof}

>>>>

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{authblk}
\usepackage{algorithm}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{algpseudocode}
\usepackage{bbm}
\usepackage{bm}
\usepackage{caption}
\usepackage{color}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{float}
\usepackage{mathtools}
\usepackage{makecell}
\usepackage{multirow}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage{comment}
\usepackage{longtable}
\usepackage{rotating}
\usepackage{xcolor}
\usepackage{fullpage}
\usepackage[utf8]{inputenc}

@@

\begin{proof}[Proof of Proposition~1]
We first derive the limiting distribution of the KS statistic under the null. 
Suppose $\hat{\theta}_n$ admits the expansion:
\begin{align}\label{eq-expan}
\hat{\theta}_n-\theta_0 = \frac{1}{n}\sum^{n}_{t=1}h(X_i;\theta_0) + 
\frac{1}{\sqrt{n}}R_n,    
\end{align}
where $h(\cdot;\theta_0)$ is the influence function with 
$\mathbb{E}[h(X_i;\theta_0)]=0$ and $R_n$ is the remainder term satisfying that
$R_n\overset{p}{\rightarrow} 0.$ Write $G_n(x):=\sqrt{n}(F_n(x) - 
F(x; \theta_0))$ 
and let $f(x;\theta)=\partial F(x;\theta)/\partial \theta$. We assume 
$\theta \in \mathbb{R}$ for ease of presentation.

\subsection{Finite-Dimensional Convergence of $G_n(x_1),\dots,G_n(x_m)$}

We assume that the sequence \(\{X_i\}\) is strictly stationary and satisfies a 
strong mixing condition.This condition ensures that the dependence between 
\(X_i\) and \(X_{i+h}\) weakens sufficiently fast as \(h\) increases.

We aim to show that for any fixed \( x_1, \ldots, x_m \), the vector \( (G_n(x_1), \ldots, G_n(x_m)) \) converges in distribution to a multivariate normal vector \( (G_{\infty}(x_1), \ldots, G_{\infty}(x_m)) \) with mean zero and covariance structure given by:
\[
\text{Cov}(G_{\infty}(x_i), G_{\infty}(x_j)) = \sum_{h=-\infty}^{\infty} \text{Cov}(\mathbf{1}\{X_0 \leq x\}, \mathbf{1}\{X_h \leq x^{\prime}\}),
\]
where $ \mathbf{1}\{\cdot\}$ is the indicator
function.

Given any $x_1,\dots,x_m$ in the domain of $F$, by the CLT for weakly dependent 
time series, we have the joint convergence of 
$V_n:=(G_n(x_1),\dots,G_n(x_m),\sqrt{n}(\hat{\theta}_n-\theta_0))$
to some Gaussian limit, with the covariance matrix being 
$\Sigma_{m+1}=\lim_{n\rightarrow+\infty}\text{Cov}(V_n)$.
Consider the empirical process $ G_n(x) = \sqrt{n} (F_n(x) - F(x)) $, where 
$ F_n(x) $ is the empirical distribution function based on $ X_1, \ldots, 
X_n $. To show finite-dimensional convergence, we need to establish that for 
any fixed $ x_1, \ldots, x_m $, the vector $ (G_n(x_1), \ldots, G_n(x_m)) $ 
converges in distribution to a multivariate normal distribution.
The 
empirical distribution function can be written as:
$
F_n(x) = \frac{1}{n} \sum_{t=1}^n \mathbf{1}\{X_i \leq x\}.
$
Therefore, the empirical process is:
$
G_n(x) = \sqrt{n} (F_n(x) - F(x)) = \frac{1}{\sqrt{n}} \sum_{i=1}^n 
(\mathbf{1}\{X_i \leq x\} - 
F(x)).
$

To establish the asymptotic distribution of $ G_n(x) $, we consider the vector 
$ (G_n(x_1), \ldots, G_n(x_m)) $:
$
(G_n(x_1), \ldots, G_n(x_m)) = \frac{1}{\sqrt{n}} \sum_{i=1}^n (\mathbf{1}\{X_i \leq x_1\} - 
F(x_1), \ldots, \mathbf{1}\{X_i \leq x_m\} - F(x_m)).
$
We calculate the covariance structure of the limiting distribution. The 
covariance between $ G_n(x) $ and $ G_n(x^{\prime}) $ is:
$
\text{Cov}(G_n(x), G_n(x^{\prime})) = \frac{1}{n} \sum_{t=1}^n \sum_{s=1}^n 
\text{Cov}(\mathbf{1}\{X_t \leq x\}, \mathbf{1}\{X_t \leq x^{\prime}\}).
$
Since $ \{X_i\} $ is strictly stationary, the covariance depends only on the 
lag $ h = |t-s| $:
$
\text{Cov}(\mathbf{1}\{X_t \leq x\}, \mathbf{1}\{X_t \leq x^{\prime}\}) = \text{Cov}(\mathbf{1}\{X_h \leq x\}, 
\mathbf{1}\{X_0 \leq x^{\prime}\}).
$
Thus, the covariance can be expressed as:
$
\text{Cov}(G_n(x), G_n(x')) = \frac{1}{n} \sum_{t=1}^n \sum_{h=-t+1}^{n-t} 
\text{Cov}(\mathbf{1}\{X_h \leq x\}, 
\mathbf{1}\{X_0 \leq x^{\prime}\}).
$

By the mixing condition, the covariances $ \text{Cov}(\mathbf{1}\{X_h \leq x\}, 
\mathbf{1}\{X_0 \leq x^{\prime}\}) $ 
decay sufficiently fast as $ h \to \infty $. Therefore, the sum converges to:
$
\lim_{n \to \infty} \text{Cov}(G_n(x), G_n(x')) = \sum_{h=-\infty}^{\infty} 
\text{Cov}(\{X_h \leq x\}, 
\mathbf{1}\{X_0 \leq x^{\prime}\}).
$

%\begin{align*}
%\Sigma_{m+1}=\begin{pmatrix}
%df & df & \cdots & df\\   
%df & df & \cdots & df\\ 
%\cdots & \cdots & \ddots & \cdots  \\ 
%df & df & \cdots & df
%\end{pmatrix}    
%\end{align*}

\subsection{Tightness of $G_n(x)$}

Moreover, we can show the tightness of the process $G_n(s)$. 
We want to show that for every $\epsilon > 0$,
$
\lim_{\delta \to 0} \limsup_{n \to \infty} \mathbb{P}\left( \omega_{G_n}(\delta) 
\geq \epsilon \right) = 0,
$
where the modulus of continuity $\omega_{G_n}(\delta)$ is defined as
$
\omega_{G_n}(\delta) = \sup_{|s - t| < \delta} |G_n(s) - G_n(t)|
$
\citep{billingsley2013convergence}.
For sufficiently small $\delta$, and leveraging the properties of weakly 
dependent sequences, we can show that
$ \sup_{|s - t| < \delta} |G_n(s) - G_n(t)| = \sup_{|s - t| < \delta} 
\sqrt{n}|(F_n(s) - F(s)) - (F_n(t) - F(t))| $
is small with high probability.
For $ |s - t| < \delta $,
$
|G_n(s) - G_n(t)| = \sqrt{n} \left| (F_n(s) - F(s; \theta_0)) - (F_n(t) - 
F(t; \theta_0)) \right|.
$
This can be decomposed as:
$
|G_n(s) - G_n(t)| = \sqrt{n} \left| (F_n(s) - F_n(t)) - (F(s; \theta_0) - 
F(t; \theta_0)) \right|.
$

Remember that $F_n(t) = \sum_{i=1}^n  \mathbf{1}\{X_i \le t\} / n$. Then, for 
$ |s - t| < \delta $, the difference $ F_n(s) - F_n(t) $ can be written as:
$ F_n(s) - F_n(t) = \frac{1}{n} \sum_{i=1}^n \left( \mathbf{1}\{X_i \leq s\} - 
\mathbf{1}\{X_i \leq t\} \right), $ or as 
$ \mathbb{E}\left[ \frac{1}{n} \sum_{i=1}^n \mathbf{1}\{ t < X_i \leq s \} 
\right] $. To provide a more precise bound on $ F_n(s) - F_n(t) $, we use 
Hoeffding's inequality, which states that for any $ t > 0 $,
$ \mathbb{P}\left( \left| \frac{1}{n} \sum_{i=1}^n \mathbf{1}\{ t < X_i \leq s 
\} - \\
\mathbb{E}\left[ \frac{1}{n} \sum_{i=1}^n \mathbf{1}\{ t < X_i \leq s \} 
\right] \right| > t \right) \leq 2 \exp\left( -2nt^2 \right). $

Since 
$ \mathbb{E}\left[ \frac{1}{n} \sum_{i=1}^n \mathbf{1}\{ t < X_i \leq s \} 
\right] = F(s; \theta_0) - F(t; \theta_0), $
we have:
$ \mathbb{P}\left( \left| \frac{1}{n} \sum_{i=1}^n \mathbf{1}\{ t < X_i \leq s 
\} - \\
(F(s; \theta_0) - F(t; \theta_0)) \right| > t \right) \leq 2
\exp\left( 
-2nt^2 \right). $
Because the true CDF is continuous, by definition, $ F(s; \theta_0) $, for any $ \epsilon > 0 
$, there esists a $ \delta > 0 $ such that for $ |s - t| < \delta $,
$ |F(s; \theta_0) - F(t; \theta_0)| < \epsilon. $ Using the bound from Hoeffding's inequality, we have:
$ \mathbb{P}\left( |F_n(s) - F_n(t) - (F(s; \theta_0) - F(t; \theta_0))| \geq 
\epsilon \right) \leq 2 \exp\left( -2n\epsilon^2 \right). $ Then, for sufficiently large $ n $ and small $ \delta $,
$ \mathbb{P}\left( \omega_{G_n}(\delta) \geq \epsilon \right) \leq 2 
\exp\left( -2n\epsilon^2 \right). $ Taking limits, we conclude:
$ \lim_{\delta \to 0} \limsup_{n \to \infty} \mathbb{P}\left( 
\omega_{G_n}(\delta) \geq \epsilon \right) = 0. $

Therefore, we have
\begin{align*}
\begin{pmatrix}
G_n(x)  \\ 
\sqrt{n}(F(x;\hat{\theta}_n)-F(x;\theta_0))
\end{pmatrix}\Rightarrow
\begin{pmatrix}
G_{\infty}(x) \\
f(x;\theta_0)U
\end{pmatrix}
\end{align*}
jointly, where $G_{\infty}(x)$ is a Gaussian process with the covariance 
function defined as
\begin{align*}
\text{Cov}(G_{\infty}(x),G_{\infty}(x'))=& 
\lim_{n\rightarrow+\infty}\frac{1}{n}\sum^{n}_{i,j=1}
\text{Cov}(\mathbf{1}\{X_i\leq x\},\mathbf{1}\{X_j\leq x'\})
\\=& \sum^{+\infty}_{h=-\infty}\text{Cov}(\mathbf{1}\{X_{h}\leq x\},
\mathbf{1}\{X_0\leq x'\}),
\end{align*}
and $U\sim N(0,s^2)$ with 
\begin{align*}
s^2=\lim_{n\rightarrow+\infty}\frac{1}{n}\sum^{n}_{i,j=1}\text{Cov}(h(X_i,
\theta_0),h(X_j;\theta_0))
= \sum^{+\infty}_{h=-\infty}\text{Cov}(h(X_{h},\theta_0),h(X_0;\theta_0)),
\end{align*}
and the covariance between $U$ and $G_{\infty}(x)$ is given by
\begin{align*}
\text{Cov}(U,G_\infty(x))=&\lim_{n\rightarrow+\infty}
\frac{1}{n}\sum^{n}_{i,j=1}\text{Cov}(h(X_i,\theta_0),\mathbf{1}\{X_j\leq x\})
\\=&\sum^{+\infty}_{h=-\infty}
\text{Cov}(h(X_{h},\theta_0),\mathbf{1}\{X_0\leq x\}).
\end{align*}
By the continuous mapping theorem, we obtain
\begin{align*}
T_n \overset{d}{\rightarrow} \sup_x |G_{\infty}(x)+f(x;\theta_0)U|.    
\end{align*}

@@

Denote by $\mathbb{E}^{(b)}$, $\text{Var}^{(b)}$ and $\text{Cov}^{(b)}$
the expectation, variance and covariance conditional on 
$\{X_i: i = 1, \ldots, n\}$ in 
the bootstrap world. Assuming that $n=kl$ with $l$ being the block size and $k$ 
being the number of blocks, the bootstrap marginal distribution is 
\begin{align*}
\rho_n^{(b)}=\frac{1}{n}\sum^{k}_{j=1}\sum^{S_j+l-1}_{i=S_j} \delta_{X_i},    
\end{align*}
where $\delta_x$ denotes a point mass at $x$, and $S_1,\dots,S_k$ are i.i.d 
uniform on $\{1,\dots,n-l+1\}$. 
Define $G_n^{(b)}(x)$ in the same way as $G_n(x)$ with $X_1, \dots, X_n$ being 
replaced by the bootstrap samples $\{X_i: i = 1, \ldots, n\}^{(b)}=\{X_1^{(b)},\dots,X_n^{(b)}\}$.

@@

\subsection{Finite-Dimensional Convergence in the Bootstrap World}

For $\sqrt{n}(F(x;\hat{\theta}_n^{(b)}) - F(x;\hat{\theta}_0))$, using the 
first-order Taylor 
expansion around $\hat{\theta}_0$ similarly to what was done in 
\citet{kunsch1989jackknife}, we have:
$
F(x;\hat{\theta}_n^{(b)}) \approx F(x;\hat{\theta}_0) + f(x; 
\hat{\theta}_0) (\hat{\theta}_n^{(b)} - \hat{\theta}_0),
$ so
$
\sqrt{n}(F(x;\hat{\theta}_n^{(b)}) - F(x;\hat{\theta}_0)) \approx \sqrt{n} 
(F(x;\hat{\theta}_0) + f(x; 
\hat{\theta}_0) (\hat{\theta}_n^{(b)} - \hat{\theta}_0) - F(x;\hat{\theta}_0)) 
\approx
f(x; 
\hat{\theta}_0) \sqrt{n} (\hat{\theta}_n^{(b)} - \hat{\theta}_0).
$

Substituting the expansion of $\hat{\theta}_n^{(b)}$:
$
\sqrt{n} (\hat{\theta}_n^{(b)} - \hat{\theta}_0) = \frac{1}{\sqrt{n}} 
\sum_{i=1}^{n} 
h(X_i^{(b)}; \hat{\theta}_0) + R_n^{(b)}.
$

Since $R_n^{(b)} \overset{p^{(b)}}{\rightarrow} 0$, 
$
\sqrt{n}(F(x;\hat{\theta}_n^{(b)}) - F(x;\hat{\theta}_0)) \approx 
f(x; \hat{\theta}_0) \left( \frac{1}{\sqrt{n}} \sum_{i=1}^{n} h(X_i^{(b)}; 
\hat{\theta}_0) \right).
$

The term $\frac{1}{\sqrt{n}} \sum_{i=1}^{n} h(X_i^{(b)}; \hat{\theta}_0)$ 
converges in distribution to a normal random variable $U$ with variance 
$s^2$.

\subsection{Tightness in Bootstrap World}
